---
title: "Untitled"
author: "Amardeep Singh"
date: "February 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r}
MBA.df <- read.csv(paste("C:\\MBA Starting Salaries Data.csv", sep=""))
View(MBA.df)
summary(MBA.df)
describe(MBA.df)
```
```{r}
boxplot(MBA.df$age,horizontal=TRUE,main="AGE")
barplot(MBA.df$age,xlab="AGE")
```
```{r}
boxplot(MBA.df$gmat_tot,horizontal=TRUE,main="gmat_tot")
barplot(MBA.df$gmat_tot,xlab="gmat_tot")
```
```{r}
boxplot(MBA.df$gmat_qpc,horizontal=TRUE,main="gmat_qpc")
barplot(MBA.df$gmat_qpc,xlab="gmat_qpc")
```
```{r}
boxplot(MBA.df$gmat_vpc,horizontal=TRUE,main="gmat_vpc")
barplot(MBA.df$gmat_vpc,xlab="gmat_vpc")
```
```{r}
boxplot(MBA.df$gmat_tpc,horizontal=TRUE,main="gmat_tpc")
barplot(MBA.df$gmat_tpc,xlab="gmat_tpc")
```
```{r}
boxplot(MBA.df$s_avg,horizontal=TRUE,main="s_avg")
barplot(MBA.df$s_avg,xlab="s_avg")
```
```{r}
boxplot(MBA.df$f_avg,horizontal=TRUE,main="f_avg")
barplot(MBA.df$f_avg,xlab="f_avg")
```
```{r}
boxplot(MBA.df$work_yrs,horizontal=TRUE,main="work_yrs")
barplot(MBA.df$work_yrs,xlab="work_yrs")
```
```{r}
boxplot(MBA.df$salary,horizontal=TRUE,main="salary")
barplot(MBA.df$salary,xlab="salary")
```
```{r}
boxplot(MBA.df$satis,horizontal=TRUE,main="satis")
barplot(MBA.df$satis,xlab="satis")
```
```{r}
attach(MBA.df)
plot(x=age,y=gmat_tot)
plot(x=age,y=gmat_qpc)
plot(x=age,y=gmat_tpc)
plot(x=age,y=s_avg)
plot(x=age,y=f_avg)
plot(x=age,y=work_yrs)
plot(x=age,y=salary)
plot(x=age,y=satis)
plot(x=sex,y=gmat_tot)
plot(x=salary,y=satis)
plot(x=salary,y=work_yrs)
plot(x=gmat_tot,y=salary)
plot(x=gmat_qpc,y=salary)
plot(x=gmat_tpc,y=salary)
plot(x=s_avg,y=salary)
plot(x=f_avg,y=salary)
```

```{r}
library(corrgram)
corrgram(MBA.df, order=TRUE, lower.panel=panel.shade,
  upper.panel=panel.pie, text.panel=panel.txt,
  main="MBA.df") 
```
Finding Placed Students
```{r}
PD.df <- MBA.df[ which(MBA.df$salary > 999), c(1,2,12,13)]
TAB1<-xtabs(~salary+sex,PD.df)
TAB1
chisq.test(TAB1)
t.test(salary ~ sex, data=PD.df)
```
Finding Unplaced Students
```{r}
NP.df <- MBA.df[ which(MBA.df$salary== 0),c(1,2,11,12,13)]
TAB11 <- xtabs(~salary+sex,NP.df)
TAB11
chisq.test(TAB11)
t.test(salary ~ sex, data=NP.df)
```

```{r}
l1<-lm(salary~age+gmat_tpc+work_yrs+frstlang,MBA.df)
summary(l1)
l2<-lm(salary~work_yrs+frstlang+gmat_tpc,MBA.df)
summary(l2)
l3<-lm(salary~quarter+work_yrs+age,MBA.df)
summary(l3)
l4<-lm(salary~gmat_tpc+sex+gmat_vpc,MBA.df)
summary(l4)
f1 <- lm(salary ~ gmat_tot + gmat_vpc + gmat_qpc + gmat_tpc , data=MBA.df)
summary(f1)
```
SUMMARY
The first language of the student plays a role in the starting salary evident by the corrgram and correlation matrices.
Comparing the people who got a job and those who didn't, a significant relationship exists between the starting salaries and the first language.
Men have been given most large starting salaries. 
The regression models show that salary little to no significance on the work years experience and first language.


