---
title: "Titanic Case Study"
author: "Amardeep Singh"
date: "February 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

```{r}
titanic.df <- read.csv(paste("Titanic Dataa.csv", sep=""))
View(titanic.df)
```

3A Total number of passengers on board the Titanic:

```{r}
length(titanic.df$Survived)
```


3B Total number of passengers who survived the sinking of the Titanic:

```{r}
length(titanic.df$Survived[titanic.df$Survived==1])
```

3C Percentage of passengers who survived the sinking of the Titanic:
```{r}

length(titanic.df$Survived[titanic.df$Survived==1])/length(titanic.df$Survived)*100
```



3D Number of first-class passengers who survived the sinking of the Titanic:
```{r}

tab1<-xtabs(~Survived+Pclass, data=titanic.df)
addmargins(tab1)
tab1[2]
```

3E Percentage of first-class passengers who survived the sinking of the Titanic:
```{r}
prop.table(tab1)[2]*100
```
3F Number of females from First-Class who survived the sinking of the Titanic:
```{r}
TABT<-xtabs(~Survived+Pclass+Sex, data=titanic.df)
addmargins(TABT)
TABT[2]
```
3G Percentage of survivors who were female:
```{r}
tab3<-xtabs(~Survived+Sex, data=titanic.df)
addmargins(tab3)
```

```{r}
prop.table(tab3)[2]*100
```


3H Percentage of females on board the Titanic who survived
```{r}
tab4<-xtabs(~Sex+Survived, data=titanic.df)
addmargins(tab4)

prop.table(tab4)[3]*100
```

3I Pearson’s Chi-squared test to test the hypothesis:
```{r}
chisq.test(tab3)
```


